Title

### 2023-04-04 main.tex
Update

Given this interpretation of the channel, 
it is easy to construct a quantum circuit that implements 
it with the help of $2n$ ancilla qubits.
The general idea is to first construct a state on the ancilla qubits
and then use this state to control gates that 
apply each Pauli operator $\sigma_{\vec{\gamma}}$ with probability $k_{\vec{\gamma}}$ 
on the principal qubits.

The circuit that does this is presented in Fig~(\ref{fig: circuit-pauli}). 
The first step in the circuit is to create the state
\begin{eqnarray}
\label{ec: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle,
\end{eqnarray}
where $b_{\vec{\gamma}}$ is in general a complex number such that 
\begin{eqnarray}
\label{ec: b}
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}.
\end{eqnarray}
Moreover $|\vec{\gamma}\rangle$ is defined as a $2n$ qubit state given by
\begin{eqnarray}
|\vec{\gamma} \rangle = |\gamma_1\rangle |\gamma_2 \rangle \cdots |\gamma_N \rangle,
\end{eqnarray}
where $|\gamma_i \rangle$ is the $2$ qubit state $|00\rangle, |01\rangle , |10\rangle$ or $|11\rangle$ when $\gamma_i = 0,1,2,3$ respectively. \\

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
 vectors $\vec{\gamma}$} \\
\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1}}} & \qw & & &\\
\lstick{ } & & & & & &\\
\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
\lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
\end{quantikz}
\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS. Hay que dejar el figure solamente con la caption y label.}} \textbf{\tbnote{Obvio éstas no serían las figuras finales, 
he visto que hacen los circuitos de forma distinta en Plos One y no usando Quantikz.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel 
on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on $2N$ ancilla qubits and then uses them to apply
all possible Pauli strings on the principal qubits
with probabilities $k_{\vec{\gamma}}$.}
\label{fig: circuit-pauli}
\end{figure}

This means that when measured in the computational base, the state given in Eq~(\ref{ec: state})
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\gamma}$. 
The circuit in Fig~(\ref{fig: circuit-pauli}) uses this fact
to apply the operations $\sigma_{\vec{\gamma}}$ over the principal qubits
with probabilities $k_{\gamma}$ by using controlled operations. 
In Fig~(\ref{fig: circuit-pauli}), the symbol shown in Fig~(\ref{fig: control})
indicates that the controlled gate is
activated if these two qubits are in the state $|\gamma_i \rangle$. 
\begin{figure}[h!]
\centering
\begin{quantikz}
& \ctrl{1} & \qw \rstick[wires=2]{$|\gamma_i \rangle$} \\
& \control{} & \qw
\end{quantikz}
\caption{{\bf Control qubits} \tbnote{Al igual que antes, esta imagen se tiene que quitar para la entrega final.} Control $|\gamma_i \rangle$ for two qubits.}
\label{fig: control}
\end{figure}

@@

\subsubsection*{Simulation for one-qubit Pauli channels}
\label{subsec: Simulation for one-qubit Pauli channels}
For the particular case of a Pauli channel on one qubit, 
the circuit that simulates it can be constructed as in Fig~(\ref{fig: citcuit-pauli-1}),
 which is a special case of figure \ref{fig: circuit-pauli}.

@@

Dynamical maps can be implemented using the same method as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{ec: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle
\end{eqnarray}

\section*{OPR Circuits}
\label{sec: OPR Circuits}
\textbf{Puntos:}
\begin{itemize}
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{eqnarray}
U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
\end{eqnarray}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\end{itemize}

\section*{OPR circuit for a Pauli map}
\label{sec: OPR circuit for a Pauli map}
\textbf{Puntos:}
\begin{itemize}
\item Use the last theorem to conclude which maps can be created using an OPR circuit.
\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. and an example that doesn't satisfy the conditions.
\item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
\end{itemize}

>>>>

Given this interpretation of the channel, 
it is easy to construct a quantum circuit that implements 
it with the help of $2n$ ancilla qubits.
The circuit that does this is presented in Fig~(\ref{fig: circuit-pauli}) and its 
first step in the circuit is to create the state
\begin{eqnarray}
\label{ec: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
in the ancilla qubits, 
where $b_{\vec{\gamma}}$ is in general a complex number such that 
\begin{eqnarray}
\label{ec: b}
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}.
\end{eqnarray}
Moreover $|\vec{\gamma}\rangle$ is defined as a $2n$ qubit state given by
\begin{eqnarray}
|\vec{\gamma} \rangle = |\gamma_1\rangle |\gamma_2 \rangle \cdots |\gamma_N \rangle,
\end{eqnarray}
where $|\gamma_i \rangle$ is the $2$ qubit state $|00\rangle, |01\rangle , |10\rangle$ or $|11\rangle$ when $\gamma_i = 0,1,2,3$ respectively. \\

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
 vectors $\vec{\gamma}$} \\
\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1}}} & \qw & & &\\
\lstick{ } & & & & & &\\
\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
\lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
\end{quantikz}
\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS. Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel 
on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on $2N$ ancilla qubits and then uses them to apply
all possible Pauli strings on the principal qubits
with probabilities $k_{\vec{\gamma}}$.}
\label{fig: circuit-pauli}
\end{figure}

This means that when measured in the computational base, the state given in Eq~(\ref{ec: state})
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\gamma}$. 
The circuit in Fig~(\ref{fig: circuit-pauli}) uses this fact
to apply the operations $\sigma_{\vec{\gamma}}$ over the principal qubits
with probabilities $k_{\gamma}$ by using controlled operations. 
The symbol shown in Fig~(\ref{fig: control})
indicates that the controlled gate is
activated if these two qubits are in the state $|\gamma_i \rangle$. 
\begin{figure}[h!]
\centering
\begin{quantikz}
& \ctrl{1} & \qw \rstick[wires=2]{$|\gamma_i \rangle$} \\
& \control{} & \qw
\end{quantikz}
\caption{{\bf Control qubits} \tbnote{Al igual que antes, esta imagen se tiene que quitar para la entrega final.} Control $|\gamma_i \rangle$ for two qubits.}
\label{fig: control}
\end{figure}

@@

\subsubsection*{Simulation for one-qubit Pauli channels}
\label{subsec: Simulation for one-qubit Pauli channels}
For the particular case of a Pauli channel on one qubit, 
the circuit that simulates it can be constructed as in Fig~(\ref{fig: citcuit-pauli-1}),
 which is a special case of Fig(\ref{fig: circuit-pauli}).

@@

Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{ec: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}

\section*{OPR Circuits}
\label{sec: OPR Circuits}
\textbf{Puntos:}
\begin{itemize}
\item As said before, to implement a Pauli dynamical map, 
we need to create the parametrized $2n$-qubit state 
$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
\item However, creating this state will in general require many rotations parametrized by $p$. 
For example, for the case of a Pauli dynamical map on 1 qubit, 
the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
In general, to create a parametrized state on $2n$ ancilla qubits will require
$2n-1$ rotations parametrized by $p$.
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{eqnarray}
U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
\end{eqnarray}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
aunque se puede y debe achicar bastante.
\end{itemize}

\section*{OPR circuit for a Pauli map}
\label{sec: OPR circuit for a Pauli map}
\textbf{Puntos:}
\begin{itemize}
\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
\item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
Lo tengo para parabolic y para depolarizing.
\end{itemize}
